---
title: "Transportation Model"
author: "Brandy Via"
output:
  pdf_document: default
  html_document:
    df_print: paged
  html_notebook:
    highlight: textmate
    theme: cerulean
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
dir.create("images")
```

# Dummy Warehouse
## Production scheduling for Heart Start.

In this problem, the total production is 220, while the total demands are only 210. So, we create a dummy warehouse. 

* The variables xij refer to production at plant i for delivery to warehouse j
* Note that the objective function coefficients include the cost of production
* As it is not possible to deliver to a nonexistent warehouse, the coefficients for the dummy warehouse have been set to zero.
* The complete formulation is below.

```
/* Objective function */
min: 622 x11 + 614 x12 + 630 x13 + 0 x14 + 641 x21 + 645 x22 + 649 x23 + 0x24;

/* Constraints */
x11 + x12 + x13 + x14  = 100;
x21 + x22 + x23 + x24  = 120;
x11 + x21 = 80;
x12 + x22 = 60;
x13 + x23 = 70;
x14 + x24 = 10;
```
```{r}
library(lpSolveAPI)
y <- read.lp("HeartStart.lp")
y
```

Solve the problem.
```{r}
solve(y)
get.objective(y)
get.variables(y)
```

